### 2010-04-01 docs/algdraft/model.tex
minor change to the model file.

\section{How to evaluate the quality of a conceptual model}

This question is posted based on the need on evaluating which conceptual model 
(e.g., OBOE, O\&M, etc) is a good one, or is better than the other. 
Unfortunately, the literature \cite{DBLP:journals/dke/Moody05, ***} shows that
there is no well-formed standard way to evaluae the quality of a conceptual model. 
On the contrary, most of the conceptual models are evaluated in an {\em ad hoc} manner. 
However, this article highlights a major principle in evaluating a conceptual model: 
a conceptual model is valuable only it is used in practice.

@@

\section{Term correspondences}
\begin{table}[htb]
\begin{tabular}{|l|l|l|l|}
\hline 
ER model & OBOE model term & O\&M term &others\\\hliine
Entity & Observation & Feature of interest & \\\hline
Characteristic & Measurement & ... & \\\hline
               & Characteristic & Property&\\\hline
               & Standard & ? & \\\hline
\end{tabular}
\end{table}

In O\&M, an {\em Observation} is defined as an action. 
It is modeled as a {\em Feature}. 
{\em Feature of Interest} is a feature that a user is interested in. 
Each feature can have properties. The {\em Property} can be {\em observed property} and other non-observed property. 
The value of {\em observed property} is obtained by an observer (e.g., a person)'s observation action.

@@

\bibliographystyle{abbrv}
\bibliography{model.bib}

>>>>

\section{How to evaluate the quality of a conceptual model (CM)}

This question is posted based on the need on evaluating which conceptual model 
(e.g., OBOE, O\&M, etc) is a good one, or is better than the other. 
Unfortunately, the literature \cite{DBLP:journals/dke/Moody05} shows that
there is no well-formed standard way to evaluae the quality of a conceptual model. 
On the contrary, most of the conceptual models are evaluated in an {\em ad hoc} manner. 
However, this article highlights a major principle in evaluating a conceptual model: 
a conceptual model is valuable only it is used in practice.

@@

\section{Term correspondences}
\begin{table}[htb]
\begin{tabular}{|l|l|l|l|}
\hline ER model & OBOE model term & O\&M term &others\\\hline
\\\hline
                      & Entity & &\\\hline
Entity             & Observation & Feature of interest & \\\hline
Characteristic & Measurement & ... & \\\hline
                       & Characteristic & Property&\\\hline
                       & Standard & ? & \\\hline
Relationship   & Context & ? & \\\hline
Value              & Standard Value & ? & \\\hline
\end{tabular}
\end{table}

In OBOE, an {\em observation} represents any {\em measurement} of some {\em characteristic} 
(attribute) of some real-world entity or phenomenon.
A {\em measurement} consists of a realized value of some characteristic of an {\em entity}, 
expressed in some well-specified units (drawn from a measurement standard) 
Observations can provide {\em context} for other observations  
(e.g. observations of spatial or temporal information would often provide context for some other observation).

In O\&M, 
An {\em observation} is an {\em action} with a {\em result} which has a value describing some phenomenon.  
The observation is modelled as a {\em Feature} within the context of the General Feature Model.  
An observation feature binds a {\em result} to a {\em feature of interest}, upon which the observation was made.  
The observed {\em property} is a property of the feature of interest. 
An observation uses a {\em procedure} to determine the value of the result, 
which may involve a sensor or observer, analytical procedure, simulation or other numerical process.  
The observation pattern and feature is primarily useful for capturing metadata associated 
with the estimation of feature properties, which is important  particularly when error in this estimate is of interest.

An {\em Observation} is defined as an action. 
It is modeled as a {\em Feature}. 
{\em Feature of Interest} is a feature that a user is interested in. 
Each feature can have properties. The {\em Property} can be {\em observed property} and other non-observed property. 
The value of {\em observed property} is obtained by an observer (e.g., a person)'s observation action.

@@

\bibliographystyle{abbrv}
\bibliography{model}
